---
title: "Generative Art"
author: "Aditi Gajjar"
format: html
editor: visual
embed-resources: true
---

## Title Art 1 - ordinary plotting functions

```{r}
library(ggplot2)
library(tibble)
library(viridis)
```

```{r}
sample_data <- function(seed = NULL, n = 100){
  if(!is.null(seed)) set.seed(seed)
  dat <- tibble(
    x0 = runif(n),
    y0 = runif(n),
    x1 = x0 + runif(n, min = -.2, max = .2),
    y1 = y0 + runif(n, min = -.2, max = .2),
    shade = runif(n), 
    size = runif(n),
    shape = factor(sample(0:22, size = n, replace = TRUE))
  )
}
```

```{r}
sample_canva <- function(seed = NULL) {
  if(!is.null(seed)) set.seed(seed)
  sample(ggthemes::canva_palettes, 1)[[1]]
}

```

**Description:** Feel free to be overly dramatic with this, if you want to - it doesn't need to involve any true art theory.

**Code Choices:**

-   A description of the code choices and how they influenced the appearance of the piece.  For example, you might say, "By setting the number of recursions to 100, we repeat the pattern 100 times in the space of the image."

## Title Art 2 - c**ompletely generative**

**Description:** Feel free to be overly dramatic with this, if you want to - it doesn't need to involve any true art theory.

**Code Choices:**

-   A description of the code choices and how they influenced the appearance of the piece.  For example, you might say, "By setting the number of recursions to 100, we repeat the pattern 100 times in the space of the image."
